Atlantis to SS for California Current sardines and hake: full fishing and climate scenario

### 2019-11-22 SardinesHakeatlantisom2SStest.Rmd
added a comment at line 1064 no change to code

#Set lbin_method to 1 - this makes the population length bins match the data bins 
#When lbin_method==1, we just comment out the binwidth, minimum, and maximum size arguments since they aren't used
stocksynthesis.data$lbin_method <- 1
stocksynthesis.data$binwidth <- "#"
stocksynthesis.data$minimum_size <- "#"
stocksynthesis.data$maximum_size <- "#"

>>>>

#Set lbin_method to 1 - this makes the population length bins match the data bins 
#When lbin_method==1, we just comment out the binwidth, minimum, and maximum size arguments since they aren't used
stocksynthesis.data$lbin_method <- 1 # this is not reading in, Lbin_method is name, but synthesis can't run if this changes from the original 3 to a 1, so I'm leaving it
stocksynthesis.data$binwidth <- "#"
stocksynthesis.data$minimum_size <- "#"
stocksynthesis.data$maximum_size <- "#"
